MATLAB: Read Me

### 2020-03-26 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Added MATLAB files. Removed Python files. Added all extra PDFs with reports

@@

Given the SDE
\begin{equation*}
\dif V_t=-\theta_tV_t\dif t+\sqrt{2\theta_t\alpha(V_t+p_t)(1-V_t-p_t)}\dif W_t,
\end{equation*}
we consider the normalized differentials $\dif\hat{t}=\frac{\dif t}{T}$, and $\dif\hat{W}_t=\frac{\dif W_t}{\sqrt{T}}$. Then, we can write the SDE as
\begin{equation*}
\dif V_t=-\alert{\theta_tT}V_t\dif\hat{t}+\sqrt{2\alert{\theta_tT}\alpha(V_t+p_t)(1-V_t-p_t)}\dif\hat{W}_t.
\end{equation*}
We conclude that, whatever the normalization constant T is, it gets absorbed by the parameter $\theta_t$ (let $\hat{\theta}_t=\theta_t T$).
\quad\\
The E-M representation is
\begin{equation*}
V_{t_{n+1}}=V_{t_{n}}-\left[\hat{\theta}_{t_n}V_{t_n}\right]\Delta s+\left[\sqrt{2\hat{\theta}_{t_n}\alpha(V_{t_n}+p_{t_n})(1-V_{t_n}-p_{t_n})}\right]\sqrt{\Delta s}\Delta\hat{W}_{t_n},\ V_{t_0}=v_0,
\end{equation*}
for $n\in\{0\dots,m-1\}$, $t_j=t_0+j\Delta s$, $t_0=0$, $t_m=1$, and $\Delta\hat{W}_{t_n}$ normal (0,1) for each $t_n$.

@@

\begin{center}
\begin{tabular}{|c|}
\toprule
{\footnotesize
\lstinputlisting{../log_dist.m}
}\\
\bottomrule
\end{tabular}
\end{center}

@@

@@

To guarantee the data homogeneity, we sample per day and not per transition. This means that each batch is composed of data corresponding to some amount of days. If we sample a total of $Z\in\N$ days, the batch corresponding to this days is
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{7}{|l|}{PATH 1}                                                                                       & ...                  & PATH Z               \\ \hline
\multicolumn{2}{|l|}{$t_n=01:10$}   & \multicolumn{2}{l|}{$t_n=01:20$}    & ... & \multicolumn{2}{l|}{$t_n=00:50$} & \multirow{4}{*}{...} & \multirow{4}{*}{...} \\ \cline{1-7}
$p(t_{n-1})$      & $p(t_{n})$      & $p(t_{n-1})$      & $p(t_{n})$      & ... & $p(t_{n-1})$     & $p(t_{n})$    &                      &                      \\ \cline{1-7}
$\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & $\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & ... & $\dot{p}(t_{n-1})$     & $\dot{p}(t_{n})$    &                      &                      \\ \cline{1-7}

@@

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../new_batch.m}
}\\
\bottomrule
\end{tabular}
\end{center}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{From $\theta_0$ to $\theta_t$:}

To ensure that the analytical solutions is always in $[0,1]$, we choose the drift parameter to be
\begin{equation*}
\theta(t) = \max\left(\theta_0,\frac{|\dot{p}(t)|}{\min(p(t),1-p(t))}\right),\quad\theta_0>0.
\end{equation*}
\quad\\
\quad\\
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../theta_t.m}
}\\
\bottomrule
\end{tabular}
\end{center}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Complete batch:}

After we created a batch with the elements $(p(t),\dot{p}(t),V(t))$, we want to add the parameter $\theta(t)$ to use in the likelihood. Following the same idea than in slide {\color{blue}\ref{cre_batch}}, the complete batch is
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{7}{|l|}{PATH 1}                                                                                       & ...                  & PATH Z               \\ \hline
\multicolumn{2}{|l|}{$t_n=01:10$}   & \multicolumn{2}{l|}{$t_n=01:20$}    & ... & \multicolumn{2}{l|}{$t_n=00:50$} & \multirow{4}{*}{...} & \multirow{4}{*}{...} \\ \cline{1-7}
$p(t_{n-1})$      & $p(t_{n})$      & $p(t_{n-1})$      & $p(t_{n})$      & ... & $p(t_{n-1})$     & $p(t_{n})$    &                      &                      \\ \cline{1-7}
$\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & $\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & ... & $\dot{p}(t_{n-1})$     & $\dot{p}(t_{n})$    &                      &                      \\ \cline{1-7}

\end{tabular}
\end{table}
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../batch_with_theta.m}
}\\
\bottomrule
\end{tabular}
\end{center}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\theta_0\cdot\alpha$:}
Recall we have $M$ paths with $N+1$ measurements each.
\begin{equation*}
\theta_0 \alpha\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (x_{i+1,j}  - x_{i,j})^2}{\sum\limits_{i=1}^{N} x_{i,j}(1-x_{i,j}) }\alert{\approx 0.021}.
\end{equation*}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../initial_guess.m}
}\\
\bottomrule
\end{tabular}
\end{center}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\theta_0$:}
Recall we have $M$ paths with $N+1$ measurements each.
\begin{equation*}
\theta_0\approx\arg\min_{\theta_0}\left[\sum_{j=1}^M\sum_{i=1}^N\left(v_{i+1,j}-v_{i,j}+\theta_{t_i}v_{i,j}\Delta t\right)^2\right].
\end{equation*}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../initial_theta.m}
}\\
\bottomrule
\end{tabular}
\end{center}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\theta_0$:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{theta_0.eps}
\end{figure}

\alert{$\theta_0\approx 1.1450
$ and $\theta_0\alpha\approx 0.021\implies\alpha\approx0.018$.}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-likelihood evaluation: CODE}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-likelihood: Plot}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../log_likelihood.eps}\quad\includegraphics[width=0.45\textwidth]{../log_likelihood_2.eps}
\end{figure}

@@

>>>>

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Code diagram:}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{../Results/project/20200320_MATLAB_Files_Graph.pdf}
\end{figure}

@@

Given the SDE
\begin{equation*}
\dif V_t=-\theta_tV_t\dif t+\sqrt{2\theta_0\alpha(V_t+p_t)(1-V_t-p_t)}\dif W_t,
\end{equation*}
we consider the normalized differentials $\dif\hat{t}=\frac{\dif t}{T}$, and $\dif\hat{W}_t=\frac{\dif W_t}{\sqrt{T}}$. Then, we can write the SDE as
\begin{equation*}
\dif V_t=-\alert{\theta_tT}V_t\dif\hat{t}+\sqrt{2\alert{\theta_0T}\alpha(V_t+p_t)(1-V_t-p_t)}\dif\hat{W}_t.
\end{equation*}
We conclude that, whatever the normalization constant T is, it gets absorbed by the parameter $\theta_t$ or $\theta_0$ (let $\hat{\theta}_t=\theta_t T$ and $\hat{\theta}_0=\theta_0 T$).
\quad\\
The E-M representation is
\begin{equation*}
V_{t_{n+1}}=V_{t_{n}}-\left[\hat{\theta}_{t_n}V_{t_n}\right]\Delta s+\left[\sqrt{2\hat{\theta}_{0}\alpha(V_{t_n}+p_{t_n})(1-V_{t_n}-p_{t_n})}\right]\sqrt{\Delta s}\Delta\hat{W}_{t_n},\ V_{t_0}=v_0,
\end{equation*}
for $n\in\{0\dots,m-1\}$, $t_j=t_0+j\Delta s$, $t_0=0$, $t_m=1$, and $\Delta\hat{W}_{t_n}$ normal (0,1) for each $t_n$.

@@

\begin{center}
\begin{tabular}{|c|}
\toprule
{\footnotesize
\lstinputlisting{../log_dist.m}
}\\
\bottomrule
\end{tabular}
\end{center}
Notice we use the function \textbf{betaln(a,b)}. It is important to compute the log directly for the beta function, and no first the beta, and after apply log.
\end{frame}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{From $\theta_0$ to $\theta_t$:}
{\small
To ensure that the analytical solutions is always in $]0,1[$, we choose the drift parameter to be
\begin{equation*}
\theta(t) = \max\left(\theta_0,\frac{\theta_0\alpha+2|\dot{p}^\epsilon(t)|}{2\min(p^\epsilon(t),1-p^\epsilon(t))}\right),\quad\theta_0>0.
\end{equation*}
\quad\\
\quad\\
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../theta_t.m}
}\\
\bottomrule
\end{tabular}
\end{center}}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{From $p_t$ to $p_t^\epsilon$:}

To ensure that $\theta(t)$ does not blow up, we truncate the forecast so it is always in $[\epsilon,1-\epsilon]$ for some $\epsilon\in(0,1/2)$.

{\small
\begin{columns}[c]

\column{.5\textwidth}
Where $p^\epsilon(t)=\begin{cases}
\epsilon\quad&\text{if}\quad p(t)<\epsilon\\
p(t)\quad&\text{if}\quad \epsilon\leq p(t)<1-\epsilon\\
1-\epsilon\quad&\text{if}\quad p(t)\geq1-\epsilon
\end{cases}$.

\column{.5\textwidth}
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../pe.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{columns}}

{\small
\begin{columns}[c]

\column{.5\textwidth}
$\dot{p}^\epsilon_t=\frac{\dif p^\epsilon}{\dif t}$. We use finite differences.

\column{.5\textwidth}
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../pe_dot.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{columns}}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Adapting the data:}

\begin{columns}[c]

\column{.2\textwidth}
We use this function to truncate the forecast, calculate its derivative, and to define the new errors ($X_t-p_t^\epsilon$) associated with the new truncated forecast.\\
We call to all this new set of data, the truncated data.

\column{.7\textwidth}
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../load_data_eps.m}
}\\
\bottomrule
\end{tabular}
\end{center}

\end{columns}

@@

\alert{This function is independent of if we are using the real data or the truncated one.} If we take a total of $Z\in\N$ days, the batch corresponding to this days is
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{7}{|l|}{PATH 1}                                                                                       & ...                  & PATH Z               \\ \hline
\multicolumn{2}{|l|}{$t_n=01:10$}   & \multicolumn{2}{l|}{$t_n=01:20$}    & ... & \multicolumn{2}{l|}{$t_n=00:50$} & \multirow{4}{*}{...} & \multirow{4}{*}{...} \\ \cline{1-7}
$p(t_{n-1})$      & $p(t_{n})$      & $p(t_{n-1})$      & $p(t_{n})$      & ... & $p(t_{n-1})$     & $p(t_{n})$    &                      &                      \\ \cline{1-7}
$\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & $\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & ... & $\dot{p}(t_{n-1})$     & $\dot{p}(t_{n})$    &                      &                      \\ \cline{1-7}

@@

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../new_batch_fixed.m}
}\\
\bottomrule
\end{tabular}
\end{center}
We call it \textbf{fixed} because, at some point, we were going to optimize the Likelihood taking random batches and increasing the size at each iteration. This idea was discarded since we have computational power enough to use all data at once.
\end{frame}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Complete batch:}
{\footnotesize
\alert{This function is independent of if we are using the real data or the truncated one.} After we created a batch with the elements $(p(t),\dot{p}(t),V(t))$, we want to add the parameter $\theta(t)$ to use in the likelihood. Following the same idea than in slide {\color{blue}\ref{cre_batch}}, the complete batch is
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{7}{|l|}{PATH 1}                                                                                       & ...                  & PATH Z               \\ \hline
\multicolumn{2}{|l|}{$t_n=01:10$}   & \multicolumn{2}{l|}{$t_n=01:20$}    & ... & \multicolumn{2}{l|}{$t_n=00:50$} & \multirow{4}{*}{...} & \multirow{4}{*}{...} \\ \cline{1-7}
$p(t_{n-1})$      & $p(t_{n})$      & $p(t_{n-1})$      & $p(t_{n})$      & ... & $p(t_{n-1})$     & $p(t_{n})$    &                      &                      \\ \cline{1-7}
$\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & $\dot{p}(t_{n-1})$ & $\dot{p}(t_{n})$ & ... & $\dot{p}(t_{n-1})$     & $\dot{p}(t_{n})$    &                      &                      \\ \cline{1-7}

\end{tabular}
\end{table}
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../batch_with_theta.m}
}\\
\bottomrule
\end{tabular}
\end{center}}

@@

%\setbeamercolor{background canvas}{bg=red!20}
%\begin{frame}\frametitle{Initial guess for $\theta_0\cdot\alpha$:}
%Recall we have $M$ paths with $N+1$ measurements each.
%\begin{equation*}
%\theta_0 \alpha\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (x_{i+1,j}  - x_{i,j})^2}{\sum\limits_{i=1}^{N} x_{i,j}(1-x_{i,j}) }\alert{\approx 0.094}.
%\end{equation*}
%
%\begin{center}
%\begin{tabular}{|c|}
%\toprule
%{\tiny
%\lstinputlisting{../initial_guess.m}
%}\\
%\bottomrule
%\end{tabular}
%\end{center}
%
%\end{frame}
%
%
%%\setbeamercolor{background canvas}{bg=white!10}
%\begin{frame}\frametitle{Initial guess for $\theta_0$ (1/2):} \label{VF}
%Recall we have $M$ paths with $N+1$ measurements each.
%\begin{equation*}
%\theta_0\approx\arg\min_{\theta_0}\left[\sum_{j=1}^M\sum_{i=1}^N\left(v_{i+1,j}-v_{i,j}+\theta_{t_i}v_{i,j}\Delta t\right)^2\right].
%\end{equation*}
%
%\begin{center}
%\begin{tabular}{|c|}
%\toprule
%{\tiny
%\lstinputlisting{../initial_theta.m}
%}\\
%\bottomrule
%\end{tabular}
%\end{center}
%
%\end{frame}
%
%
%%\setbeamercolor{background canvas}{bg=white!10}
%\begin{frame}\frametitle{Initial guess for $\theta_0$ (2/2):}
%
%\begin{figure}[ht!]
%\centering
%\includegraphics[width=0.35\textwidth]{../Results/initial_guess/initial_theta_1.eps}\quad\quad\quad
%\includegraphics[width=0.35\textwidth]{../Results/initial_guess/initial_theta_2.eps}
%\caption{On the left, we use the value function defined in slide {\color{blue}\ref{VF}}. On the right, we substitute in the value function $\theta_t$ by $\theta_0$ and plot that \textit{new value function}. We use the value from the left plot.}
%\end{figure}
%\alert{$\theta_0\approx 0.67
%$ and $\theta_0\alpha\approx 0.094\implies\alpha\approx0.15$.} If we use the plot on the right, then $\theta_0\approx1.23$ and $\alpha\approx0.08$.
%
%\end{frame}

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Initial guess for $\theta_0\cdot\alpha$: Quadratic variation}

Recall we have $M$ paths with $N+1$ measurements each. Depending on the SDE we are using, we have the two approximations:
{\footnotesize
\begin{equation*}
X_t:\theta_0^*\alpha^*\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (\Delta X_{i,j})^2}{\sum\limits_{i=1}^{N} (X_{i,j})(1-X_{i,j})},\quad V_t:\theta_0^*\alpha^*\approx \frac{1}{2M\Delta t} \sum\limits_{j=1}^M \frac{ \sum\limits_{i=1}^{N} (\Delta V_{i,j})^2}{\sum\limits_{i=1}^{N} (V_{i,j}+p_{i,j})(1-V_{i,j}-p_{i,j})}
\end{equation*}
}
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../initial_guess.m}
}\\
\bottomrule
\end{tabular}
\end{center}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\theta_0$ (1/2): Mean least squares} \label{VF}
Recall we have $M$ paths with $N+1$ measurements each. If we assume $\theta_t^\epsilon=\theta_0$ for $t\in[0,T]$, then we have
\begin{equation}
\theta_0^*\approx\arg\min_{\theta_0}{\left[\sum_{j=1}^M\sum_{i=1}^N\left(V_{i+1,j}-V_{i,j}(1-\theta_0\Delta t)\right)^2\right]}.
\label{Eq-1}
\end{equation}

%\begin{center}
%\begin{tabular}{|c|}
%\toprule
%{\tiny
%\lstinputlisting{../initial_theta_0.m}
%}\\
%\bottomrule
%\end{tabular}
%\end{center}

As problem (\ref{Eq-1}) is convex, we can formulate the equivalent problem using derivatives
\begin{equation*}
\theta_0^*\approx\frac{1}{\Delta t\cdot M}\sum_{j=1}^M\frac{\sum_{i=1}^NV_{i,j}(V_{i,j}-V_{i+1,j})}{\sum_{i=1}^NV_{i,j}^2}.
\end{equation*}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\theta_0$ (2/2): Mean least squares}

As we need to assume that $\theta_t^\epsilon=\alert{c}\in\R^+$ in order to use correctly the estimator (\ref{Eq-1}), we define $\epsilon,\gamma\in\R^+$, and estimate $\frac{\theta_0\alpha}{\delta}$ using data which original forecast satisfies $p_i\notin(\epsilon,1-\epsilon)$ and $\theta_0$ using data which original forecast satisfies $p_i\in[\gamma,1-\gamma]$. The full explanation can be found in slides \textbf{20200308 - Initial Guess.pdf}.

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../mean_regression_eps.m}
}\\
\bottomrule
\end{tabular}
\end{center}
To create this specific data sets, we use the functions \textbf{create\_samples\_eps.m} ($\epsilon$-data) and \textbf{create\_samples\_minus\_eps.m} ($\gamma$-data).

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Initial guess for $\delta$:}

We have that, for almost all days, at time $t=t_0$, $X(t_0)\neq p(t_0)$ and then $V(t_0)\neq0$. However, by forecast construction, there should exist a time $t_{-\delta}<t_0$ such that $V(t_{-\delta})=0$.\\
\quad\\
We extrapolate linearly $p(t)$ so we can evaluate $p(t_{-\delta})$, and assume that $V(t_{-\delta})=0$. Then, for each day $j$, we have an initial transition $(V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta)$. We assume again that it is Beta and apply the same moment matching as for the rest of transitions. With our initial guess for $\bm{\theta}$, we can construct our initial guess for $\delta$ solving the problem

\begin{equation*}
\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
\label{likelihood_delta}
\end{equation*}

See slides \textbf{20200319 - Time delta} for very detailed information.\\
\quad\\
We use $\delta=\SI{5.5}{\hour}$.

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-likelihood evaluation (1/2): CODE}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Log-likelihood evaluation (2/2):}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood.eps}
\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood_refined.eps}
\includegraphics[width=0.32\textwidth]{../Results/likelihood/Log-Likelihood_more_refined.eps}
\caption{We use the code \textbf{plotLogLikelihood.m} to create this plots. We used about 18 thousand transitions, and we can also see the initial guess.}
\end{figure}

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Summing-up:}

\begin{enumerate}

\item Initial guess: From quadratic variation and using all the data we get $\hat{\theta}_0\times\hat{\alpha}$. Choosing some appropiate $\gamma$, from mean least squares we get $\hat{\theta}_0$, then we also get $\hat{\alpha}$.\\
Also, from mean least squares we can estimate $\epsilon^*$, using that the least squares estimator estimates $\frac{\theta_0\alpha}{\epsilon}$ for some appropriate $\epsilon$.\\
Finally, using the pair $(\hat{\theta}_0,\hat{\alpha})$, we can obtain $\hat{\eta}$ and $\hat{\delta}$.

\item Optimal parameters: Using the training data and the initial point $(\hat{\theta}_0,\hat{\alpha})$, we can find the optimal pair $(\theta_0^*,\alpha^*)$ using the MLE. With this new pair, we can find $\eta^*$ and $\delta^*$.

\end{enumerate}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Values for the parameters:}

\begin{table}[]
\begin{tabular}{cccccc}
\toprule
$\hat{\theta}_0$ & $\hat{\alpha}$ & $\hat{\eta}$ & $\hat{\delta}$ & $\gamma$ & $\epsilon$ \\
\midrule
$1.63$ & $0.06$ & *not apply* & $\SI{220}{\min}$ & $0.3$ & $0.018$ \\
\bottomrule
\end{tabular}
\end{table}
$\eta^{ini}$ is not relevant here because we do not need to remove any data to find $\delta^{ini}$.
\begin{table}[]
\begin{tabular}{ccccc}
\toprule
$\theta_0^{*}$ & $\alpha^{*}$ & $\eta^{*}$ & $\delta^{*}$ \\
\midrule
$3.91$ & $0.02$ & $0.1$ & $\SI{220}{\min}$ \\
\bottomrule
\end{tabular}
\end{table}
Notice that $\hat{\delta}=\delta^*$. However, to obtain $\delta^*$ we had to remove all initial errors larger than $\eta^*$, and in this way, we reduced the variance of the initial error. This has sense since $\theta^*_0\alpha^*<\hat{\theta}_0\hat{\alpha}$.

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Paths and bands for optimal values (1/4):}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../Results/paths_testing_days/optimal_value/1.eps}\quad
\includegraphics[width=0.4\textwidth]{../Results/bands_testing_days/optimal_value/1.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Paths and bands for optimal values (2/4):}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../Results/paths_testing_days/optimal_value/2.eps}\quad
\includegraphics[width=0.4\textwidth]{../Results/bands_testing_days/optimal_value/2.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Paths and bands for optimal values (3/4):}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../Results/paths_testing_days/optimal_value/3.eps}\quad
\includegraphics[width=0.4\textwidth]{../Results/bands_testing_days/optimal_value/3.eps}
\end{figure}

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Paths and bands for optimal values (4/4):}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{../Results/paths_testing_days/optimal_value/4.eps}\quad
\includegraphics[width=0.4\textwidth]{../Results/bands_testing_days/optimal_value/4.eps}
\end{figure}
\end{frame}
